Value-Suppressing Uncertainty Maps

### 2017-03-22 paper/template.tex
More DM fixes.

Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \textbf{uncertainty-aware decisions}--- that is, the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \textbf{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset. Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map--- a relation, in terms of visual variables, between a 2-tuple $(value$,$uncertainty)$ and a set of marks. The design of bivariate maps is difficult and, due to the interference and interplay between different visual variables, often leads to maps with few discriminable categories.

>>>>

Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \textbf{uncertainty-aware decisions}--- that is, the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \textbf{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset. Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map--- a relation, in terms of visual variables, between 2-tuples $(\text{value}, \text{uncertainty})$ and mark properties. The design of bivariate maps is difficult and, due to the interference and interplay between different visual variables, often leads to maps with few discriminable categories.
